---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%'
)
```

# enum

<!-- badges: start -->
<!-- badges: end -->

`enum` enumerates all partitions of a graph into `k` connected pieces within given piece-size bounds.
It is a direct R translation of the Julia [enumerator](https://github.com/zschutzman/enumerator) package by Zachary Schutzman, reimplemented using [igraph](https://r.igraph.org/).

## Installation

```r
# install.packages('pak')
pak::pak('christopherkenny/enum')
```

## Usage

### Grid partitions

The primary interface partitions rectangular grids under rook or queen contiguity.
Each column of the returned matrix is one valid partition; each row corresponds to a grid cell in row-major order, with integer values giving part membership.

```{r grid}
library(enum)

# All ways to split a 3x3 grid into 3 rook-connected pieces of size 3
enum_partitions(3, 3, num_parts = 3, min_size = 3, max_size = 3)
```

For example, one valid partition of the 3×3 grid

```
1 1 2
1 2 2
3 3 3
```

is stored as the column `c(1, 1, 2, 1, 2, 2, 3, 3, 3)`.

We can also count the number, which is faster if you don't need the full output:

```{r countgrid}
enum_count_partitions(3, 3, num_parts = 3, min_size = 3, max_size = 3)
```

### Graph partitions

For arbitrary graphs, pass an `igraph` object (or an [`adj` object](https://alarm-redist.org/adj/)):

```{r graph}
library(igraph)

g <- make_ring(6)
enum_partitions_graph(g, num_parts = 2, min_size = 3, max_size = 3)
```
